Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-23 main.tex
done editing Sec. VII

Two heuristics rely on an ordering of tasks based on the bottom level of tasks, with the objective
of minimizing the makespan and hence scheduling critical tasks first. The third one, \heftmm,
goes one step further and handles tasks in an order dictated by an efficient traversal
of the graph in terms of memory requirements, hence reducing the memory used
by the schedule. Experimental results on a large set of workflows coming from real-life applications
demonstrate that the memory-aware heuristics are  successfully producing valid schedules. 
In the most memory-constrained setting, \heftmm succeeds to schedule even the largest workflows,
while other heuristics return invalid schedules exceeding the memory capacity of processors. 
It comes at a price of a makespan that is not quite as good as the one obtained by \heftbl
and \heftblc, which focus on makespan by ordering tasks by bottom level. 
As expected, the baseline \heft that is not memory aware returns invalid schedules in almost
all settings, except for very small workflows.

@@

Another key contribution is that we have adapted these heuristics for a dynamic setting, where exact
task parameters (execution times and memory requirements) are not know in advance. 
We have implemented a runtime system that interacts with the scheduler, returning exact
parameter values once a task arrives in the system, while only estimates are known for future tasks. 
Some preliminary experiments have been conducted in this setting, and demonstrated that
it is necessary to adapt the schedule on the fly in order to avoid an execution failure because
of a shortage in memory. To the best of our knowledge, this is the first study of adaptive
algorithms accounting for memory constraints.

This work could be extended in several directions. First, the model could be refined to include
heterogeneous bandwidths, while we consider a homogeneous communication network. 
More importantly, it would be interesting to consider other types of variability, for instance
if new tasks appear in the graph (or disappear), or if there is variability in the platform, 
with processors arriving and departing. We believe that we could adapt the current approach
by recomputing schedules on the fly, and we plan to perform a new set of experiments
to further assess the impact of dynamic scheduling.

>>>>

Two heuristics rely on an ordering of tasks based on the bottom level of tasks, with the objective
of minimizing the makespan and hence scheduling critical tasks first. The third one, \heftmm,
goes one step further and handles tasks in an order dictated by an efficient traversal
of the graph in terms of memory requirements, hence reducing the memory used
by the schedule. Experimental results on a large set of workflows coming from real-life applications
demonstrate that the memory-aware heuristics produce valid schedules successfully. 
In the most memory-constrained setting, \heftmm succeeds to schedule even the largest workflows,
while the other heuristics return invalid schedules that exceed the memory capacity. 
This advantage of \heftmm comes at the price of worse makespans than with \heftbl
and \heftblc. % which focus on makespan by ordering tasks by bottom level. 
As expected, the baseline \heft, which is not memory-aware, returns invalid schedules in almost
all settings, except for very small workflows.

@@

Another key contribution is that we have adapted these heuristics for a dynamic setting, where exact
task parameters (execution times and memory requirements) are not known in advance. 
We have implemented a runtime system that interacts with the scheduler, providing exact
parameter values once a task arrives in the system, while only estimates are known for future tasks. 
Some preliminary experiments have been conducted in this setting and demonstrated that
it is necessary to adapt the schedule on the fly in order to avoid an execution failure because
of a memory shortage. To the best of our knowledge, this is the first study of adaptive
algorithms accounting for memory constraints.

This work could be extended in several directions. First, the model could be refined to include
heterogeneous bandwidths, while we consider a homogeneous communication network. 
More importantly, it would be interesting to consider other types of variability, for instance
if new tasks appear in (or disappear from) the workflow graph, or if there is variability in the platform, 
with processors arriving and departing. We believe that we could adapt the current approach
by recomputing schedules on the fly, and we plan to perform a new set of experiments
to further assess the impact of dynamic scheduling.
